---
title: "My Portfolio"
author: "Jens Ruhof"
date: "2/10/2021"
output: html_document
---

<!-- # ```{r setup, include=FALSE} -->
<!-- # knitr::opts_chunk$set(echo = TRUE) -->
<!-- # ``` -->

## My corpus

To Do: Insert and fix readme text here

#### import library's
```{r}
library(tidyverse)
library(spotifyr)
library(dplyr)
library(fmsb)
```

### Get eminem complete playlist
``` {r}
 Eminem <- get_playlist_audio_features("", "6E8sLG3bm1meTRj8n5l0ll")

mean_eminem <- Eminem %>%
  summarise(
    mean_danceability = mean(danceability),
    mean_energy = mean(energy),
    mean_speechiness = mean(speechiness),
    mean_acousticness = mean(acousticness),
    mean_instrumentalness = mean(instrumentalness),
    mean_liveness = mean(liveness),
    mean_valence = mean(valence)
    
  )
mean_eminem
```
#### Least popular songs of eminem according to spotify.

``` {r}

Eminem %>% 
  group_by(track.popularity) %>% 
  filter(track.popularity <= "35") %>%
  ggplot(aes(x = track.name, y = track.popularity)) + 
  geom_col(aes(fill = track.album.name)) +
  labs(x= "Track name", y= "Popularity") + 
  ggtitle("What are the least popular Eminem songs in this playlist?", "Popularity ranking < 35 in a specific playlist") +
  theme(axis.text.x = element_text(angle = 90)
        ,legend.position = "right")

```
A thing to note already is that the paul skit appears on multiple albums and that his skits often aren't very popular. A reason for this could be that these skits aren't songs and are often a story within the album. An example is the paul skit or skits I should say. These skits, since there are multiple named Paul are a reference to his music manager Paul Rosenberg in which eminem often features a snippet of a phone conversation with some information about the album.


#### Most popular eminem songs according to spotify
``` {r}

Eminem %>% 
  group_by(track.popularity) %>% 
  filter(track.popularity >= "75") %>%
  ggplot(aes(x = track.name, y = track.popularity)) + 
  geom_col(aes(fill = track.album.name)) +
  labs(x= "Track name", y= "Popularity") + 
  ggtitle("What are the most popular Eminem songs in this playlist?", "Popularity ranking > 75 in a specific playlist") +
  theme(axis.text.x = element_text(angle = 90)
        ,legend.position = "right")


```
An interesting thing to see here is that all of his major albums have at least one song with a high popularity with personally one of his best albums "recovery" having two in it. I would like to delve into popularity per album and compare the populartiy with other things spotify measures later on.



``` {r}
# create data
data <- rbind(rep(1,1) , rep(0,10) , mean_eminem)

# Make radar
radarchart(data, axistype=1 , 
 
    # Polygon changes
    pcol="black", 
    pfcol = rgb(0,72,105,165, max = 255), 
    plwd=2 ,
 
    #Grid changes
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,1,0.2), cglwd=0.8,
 
    # Labels and title
    vlcex=0.8,
    title = "mean values Eminem songs")

```

<!-- ## Including Plots -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. -->



